%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command
\newcommand{\red}[1]{{\color{red} #1}}
\overrideIEEEmargins                                      % Needed to meet printer requirements.

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\input{include/packages}

\title{\LARGE \bf
A Framework for Interaction Control of Mobile Manipulators
}


\author{Giuseppe Rizzi, Jen Jen Chung, Abel Gawel, Marco Tognon, Lionel Ott and Roland Siegwart% <-this % stops a space
\thanks{This work was supported by the European Union H2020 program under project PILOTING No H2020-ICT-2019-2 871542.}
\thanks{The authors are with the Autonomous Systems Lab, ETH Z\"urich, Z\"urich 8092, Switzerland. {\tt\small\{grizzi; chungj; gawela; mtognon; lioott; rsiegwart\}@ethz.ch}}%
}


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In this work we investigate and deploy stochastic control techniques for the challenging task of mobile manipulation. By their nature, manipulation tasks necessitate environment interactions which require the handling of non-differentiable switching contact dynamics. These dynamics represent a strong limitation for traditional gradient-based optimization methods such as Model Predictive Control (MPC) and Differential Dynamic Programming (DDP). \emph{Sampling-based} techniques alleviate these constraints. In this work we proposed a novel framework for safe robotic manipulation of movable objects. We combine sampling methods for solving complex manipulation tasks with a mobile manipulator, together with \emph{Control Barrier Functions} and \emph{Passivity Theory} that, thanks to formal stability guarantees, enhance the safety and robustness of the method. The proposed controller enables robust real-time deployment of stochastic control. We deploy the algorithm on a 10-DOF mobile manipulator robot and a conventional CPU. A video of the experiments can be found at \url{new-url-here}.
  
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{include/sections/introduction}

\input{include/sections/problem_formulation}

\input{include/sections/preliminaries}

\input{include/sections/control_method}

\input{include/sections/practical_aspects}

\input{include/sections/experiments}

\input{include/sections/conclusions}


% \addtolength{\textheight}{-13.5cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{ACKNOWLEDGMENT}

% This work was supported in part by ABB Corporate Research, the Luxembourg National Research Fund (FNR) 12571953 and the ETH Foundation with an unrestricted gift from Huawei Technologies.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendices
\input{include/sections/appendix}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.








\end{document}
